---
title: "Code Book"
author: "Petra Stone"
date: "2/22/2017"
output: html_document
bibliography: bibliography.bibtex
link-citations: true
nocite: | 
  @jorge_esann2013_2
---

```{r setup, include=FALSE}
    knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
    knitr::opts_knit$set(root.dir="/Users/petra/githubstuff/getdata")
```

### Summary of `tidyData.txt`

This data set presents the means for 66 variables from the original data set grouped by subject and activity.
The original data set [@jorge_esann2013_2] was based on 30 subjects performing activities of daily living while carrying a waist-mounted smartphone with embedded inertial sensors.

```{r echo=F}

    require(knitr)

    kable( data.frame( row.names=c("Dimensions","Identifiers","Observations","Variables"),
                       "Info"= c(
                           "180 rows x 68 columns",
                           "`Subject` `Activity`",
                           180,
                           66 
                       ),
                        "Notes"=c(
                            "66 Variables and 2 Identifier columns",
                            "Identifier columns for the subject and the activity the subject performed.<br>`Subject`: Integer from 1 to 30.<br>`Activities`: Walking, Walking Upstairs, Walking Downstairs, Sitting, Standing, Lying Down",
                            "Each observation (row) is a combination of subject and one of the 6 activities for 30 subjects",
                            "Each variable (column) is the mean of 66 variables extracted from the original data set"
                            
                        )
           
           ) )

```


### Variables in `tidyData.txt`

```{r echo=F}

    vars <- c(
        "`Accel`","`Gyro`","`Body`","`Gravity`","`Jerk`",
        "`Magtd`","`X`,`Y`,`Z`","`FFT`",
        "Mean",
        "Std",
        "MeanOf"
    )
    descriptions <- c(
        "Measurement from the accelerometor sensor",
        "Measurement from the gyroscope sensor",
        "Body acceleration component derived from accelerometer measurement",
        "Gravity acceleration component derived from accelerometer measurement",
        "Body linear acceleration and angular velocity",
        "Magnitude of `Body`, `Gravity` and `Jerk` signals",
        "Measurement taken along the X, Y or Z axis of the accelerometer and gyro",
        "The FFT suffix indicates that a fast fourier transform was applied to the measurement",
        "Mean calculated in original study",
        "Standard Deviation calculated in original study",
        "Mean by group (person and activity)"
    )
    
    notes <- c(
        "Filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20Hz",
        "Filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20Hz",
        "Filtered using a low pass Butterworth filter with a corner frequency of 0.3Hz.",
        "Filtered using a low pass Butterworth filter with a corner frequency of 0.3Hz.",
        "Derived from `Body` and `Gyro` measurements",
        "Calculated using the Euclidean norm",
        "-",
        "Fast fourier transform",
        "Mean was calculated at windows of 2.5sec from raw measurements",
        "Std deviation was calculated at windows of 2.5sec from raw measurements",
        "-"
    )
    
    kable( data.frame("Component"=vars, "Description"=descriptions,"Notes"=notes), caption="Meanings of Components of Variable Names")
    
    

```

### Examples
```{r echo=F}
    
    vars <- c(
        "`MeanOfBodyAccelMeanZ`","`MeanOfGravityAccelMagtdStd`","`MeanOfBodyGyroJerkMeanX`","`MeanOfBodyAccelStdYFFT`"
    )
    
    description <- c(
        "Mean (by Subject and Activity) of Mean of Body acceleration on the Z axis.",
        "Mean (by Subject and Activity) of Standard deviation of Gravity acceleration magnitude",
        "Mean (by Subject and Activity) of Mean of Jerk signal on X axis (originally derived from both accel and gyro sensors)",
        "Mean (by Subject and Activity) of Mean of Body acceleration on the Y axis with a fast fourier transform"
    )
    kable( data.frame("Variable"=vars, "Description"=description), caption="Some examples of interpreting variable names")
```

### Full List of Variables

```{r echo=F}
    tidyData <- read.csv("tidyData.csv")
    kable( data.frame( "Variables"= paste("`", names(tidyData[3:68]),"`") ), row.names = seq(1,66) )
```

### References